Human Judgement Forecasting of COVID-19 in the UK

### 2023-03-01 manuscript/manuscript.tex
update manuscript

\citet{bosseTransformationForecastsEvaluating2023} suggested to transform forecasts and observations using the natural logarithm prior to applying the WIS in order to better reflect the exponential nature of the underlying disease process. We therefore also compute WIS values after transforming all forecasts and observations using the function $f\colon x \to \log (x + 1)$. In the following, we refer to WIS scores obtained without a transformation as "scores on the natural scale", and WIS values obtained after log-transforming forecasts and observations as "scores on the log scale".

@@

>>>>

\citet{bosseTransformationForecastsEvaluating2023} suggested to transform forecasts and observations using the natural logarithm prior to applying the WIS in order to better reflect the exponential nature of the underlying disease process. We therefore also compute WIS values after transforming all forecasts and observations using the function $f\colon x \to \log (x + 1)$. In the following, we refer to WIS scores obtained without a transformation as "scores on the natural scale", and WIS values obtained after log-transforming forecasts and observations as "scores on the log scale". To make results easier to interpret, we also report normalised scores. We normalised scores for a given target (cases or deaths) and scale (natural or log) by calculating a Z-score, i.e. by subtracting the mean of all scores for the same target and scale, and dividing by the standard deviation.

@@

Overall scores for all forecasting approaches (Forecast Hub ensemble, direct crowd forecasts, $R_t$ crowd forecasts, combined crowd forecast) are very close to each other.
